Clinical prediction using similarity-based cohorts: A scoping review

### 2023-04-05 docs/Manuscript/Manuscript.Rmd
link to zotero group library

We conducted all searches over 2021 July 19–22. We tentatively excluded results from Google Scholar because they were missing abstracts, and later agreed to discard these results due to the lack of reproducibility of the search. We organized the remaining results into a Zotero collection with one subcollection for each database. We then imported the pooled results to Covidence, which merged some duplicate entries.

@@

Data collected or encoded for included studies are publicly available in two Google Sheets. Code used to analyze these data and generate this manuscript is publicly available in a GitHub repository.

* Bibliographic and methodological properties of included studies: <https://docs.google.com/spreadsheets/d/1tpWMhYH2pyRT55K7n2J2XFs-kEV_JTuCDmXzJ4BBgNo/>
* Terminology and composite techniques of included studies: <https://docs.google.com/spreadsheets/d/1xvDJwiLBoI2oz8fxHJ5MjNmiju_RAlK7RJv-wXe1DAs/>
* Code used to perform analyses and prepare the manuscript: <https://github.com/corybrunson/imsr>

@@

These totaled 1,422 sources from all platforms. We organized the full results in a Zotero collection alongside the seed set and created a single folder for the 25 results reviewed in detail.

>>>>

We conducted all searches over 2021 July 19–22. We tentatively excluded results from Google Scholar because they were missing abstracts, and later agreed to discard these results due to the lack of reproducibility of the search. We organized the remaining results into a public Zotero collection with one subcollection for each database. We then imported the pooled results to Covidence, which merged some duplicate entries.

@@

Search results are publicly available in a Zotero group library.
Data collected or encoded for included studies are publicly available in two Google Sheets.
Code used to analyze these data and generate this manuscript is publicly available in a GitHub repository.

* Search results, included studies, and other bibliography: <https://www.zotero.org/groups/5017571/imsr/>
* Bibliographic and methodological properties of included studies: <https://docs.google.com/spreadsheets/d/1tpWMhYH2pyRT55K7n2J2XFs-kEV_JTuCDmXzJ4BBgNo/>
* Terminology and composite techniques of included studies: <https://docs.google.com/spreadsheets/d/1xvDJwiLBoI2oz8fxHJ5MjNmiju_RAlK7RJv-wXe1DAs/>
* Code used to perform analyses and prepare the manuscript: <https://github.com/corybrunson/imsr>

@@

These totaled 1,422 sources from all platforms. We organized the full results in a public Zotero collection alongside the seed set and created a single folder for the 25 results reviewed in detail.
